Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-03 eurocg/paper.tex
affiliation stuff
prelims

\affil[1]{Algorithms and Complexity Group, TU Wien, Vienna, Austria}
%\affil[2]{Algorithms and Complexity Group, TU Wien, Vienna, Austria} %\texttt{fklute@ac.tuwien.ac.at}}
%\affil[3]{Algorithms and Complexity Group, TU Wien, Vienna, Austria \texttt{}}
%\affil[4]{Algorithms and Complexity Group, TU Wien, Vienna, Austria} %\texttt{noellenburg@ac.tuwien.ac.at}}
%\affil[5]{Algorithms and Complexity Group, TU Wien, Vienna, Austria \texttt{}}
%mandatory. First: Use abbreviated first/middle names. 
%Second (only in severe cases): Use first author plus 'et. al.'
\authorrunning{F. Klute and M. N\"ollenburg}

@@

Let $ G $ be a \emph{simple graph} with edge set $ S = \{s_1,\dots,s_m\}$ and $ \Gamma $ a straight line drawing of $ G $ in the plane. We call $ \Gamma $ \emph{$ k $-plane} if every edge $ s_i \in S $ is crossed by at most $ k $ other edges from $ S $ in $ \Gamma $. The \emph{intersection graph} $ C = (V,E) $ of $ \Gamma $ is the graph containing a vertex $v_i$ in $ V $ for every $ s_i \in S $ and an edge $ v_i v_j \in E $ between vertices $ v_i, v_j \in V $ if the corresponding edges $ s_i, s_j \in S $ intersect in $ \Gamma $. Observe that the intersection graph $ C $ of a $ k $-plane drawing $ \Gamma $ has maximum degree $ k $. It is known that every planar graph is representable as the intersection graph of line segments~\cite{chalopin2009every}.

\fabian{This part has to be adapted once the intro is fixed}

We define a \emph{partial edge drawing} (\ped) $ \Gamma' $ of $ G $ as a drawing using the same embedding as $ \Gamma $, but edges are drawn as \emph{stubs}, i.e., we do not depict an edge $ s_i \in S $ by a line segment connecting the two vertices, but remove the middle part of the edges such that no two stubs intersect in $ \Gamma' $. We call a \ped $ \Gamma' $ \emph{symmetric} if for every edge $ s_i s_j \in S $ its two stubs have equal lengths in $ \Gamma' $. Finally we define the problem \maxsped as finding a symmetric \ped $ \Gamma' $ of $ G $ where the sum of the lengths of the stubs is maximized. This is also known as ink maximization~\cite{bcgkmn-pped-17}.

\martin{Maybe we don't need the above paragraph as PED, SPED, maxSPED are all somewhat defined in the introduction}

>>>>

\affil[1]{Algorithms and Complexity Group, TU Wien, Vienna, Austria\\ \texttt{[fklute|noellenburg|]@ac.tuwien.ac.at}}
%\affil[2]{Algorithms and Complexity Group, TU Wien, Vienna, Austria} %\texttt{fklute@ac.tuwien.ac.at}}
%\affil[3]{Algorithms and Complexity Group, TU Wien, Vienna, Austria \texttt{}}
%\affil[4]{Algorithms and Complexity Group, TU Wien, Vienna, Austria} %\texttt{noellenburg@ac.tuwien.ac.at}}
%\affil[5]{Algorithms and Complexity Group, TU Wien, Vienna, Austria \texttt{}}
%mandatory. First: Use abbreviated first/middle names. 
%Second (only in severe cases): Use first author plus 'et. al.'
\authorrunning{M. Höller, F. Klute, S. Nickel, M. N\"ollenburg, and B. Schreiber}

@@

Throughout the paper let $ G $ be a \emph{simple graph} with edge set $ S = \{s_1,\dots,s_m\}$ and $ \Gamma $ a straight line drawing of $ G $ in the plane. We call $ \Gamma $ \emph{$ k $-plane} if every edge $ s_i \in S $ is crossed by at most $ k $ other edges from $ S $ in $ \Gamma $. The \emph{intersection graph} $ C = (V,E) $ of $ \Gamma $ is the graph containing a vertex $v_i$ in $ V $ for every $ s_i \in S $ and an edge $ v_i v_j \in E $ between vertices $ v_i, v_j \in V $ if the corresponding edges $ s_i, s_j \in S $ intersect in $ \Gamma $. Observe that the intersection graph $ C $ of a $ k $-plane drawing $ \Gamma $ has maximum degree $ k $. Also it is known that every planar graph is representable as the intersection graph of line segments~\cite{chalopin2009every}.

%\fabian{This part has to be adapted once the intro is fixed}
%
%We define a \emph{partial edge drawing} (\ped) $ \Gamma' $ of $ G $ as a drawing using the same embedding as $ \Gamma $, but edges are drawn as \emph{stubs}, i.e., we do not depict an edge $ s_i \in S $ by a line segment connecting the two vertices, but remove the middle part of the edges such that no two stubs intersect in $ \Gamma' $. We call a \ped $ \Gamma' $ \emph{symmetric} if for every edge $ s_i s_j \in S $ its two stubs have equal lengths in $ \Gamma' $. Finally we define the problem \maxsped as finding a symmetric \ped $ \Gamma' $ of $ G $ where the sum of the lengths of the stubs is maximized. This is also known as ink maximization~\cite{bcgkmn-pped-17}.
%
%\martin{Maybe we don't need the above paragraph as PED, SPED, maxSPED are all somewhat defined in the introduction}
